Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-06 tex/main.tex
Minor changes/addition to front-end section.

The translation modifies $\varphi$ in two main ways. First, it restricts the
quantification on function definitions for $\con{f}$ to the corresponding
uninterpreted type $\fargsort{\con{f}}$ and inserts appropriate coercions
$\fargx{\con{f}}{i}$. Second, it augments $\varphi$ with additional constraints
$\exists a : \fargsort{\con{f}}.\;\, \vecfarg{\con{f}}( a ) \teq \vec t$; these
ensure that the restricted definition for $\con{f}$ covers all relevant tuples
of terms, namely the ones for which an $\con{f}$ application exists and is
relevant to the satisfiability of the current branch of $\varphi$.
\jb{what does ``current branch of'' mean? can we drop it / rephrase it / vague
it up?}

@@

{\small
\begin{verbatim}
(define-fun-rec s ((x Int)) Int (ite (<= x 0) 0 (s (- x 1))))
(assert (> (s x) 100))
(check-sat)
\end{verbatim}
}

When reading this input,
\cvc adds the (annotated) quantified formula $\forallf{\con{s}} x.\;\, \con{s}( x ) \teq \lite\bigl( x \leq 0, 0, \con{s}( x-1 )\bigr)$ to its list of assertions,
which after rewriting becomes $\forallf{\con{s}} x.\;\, \lite\bigl( x \leq 0, \con{s}( x ) \teq 0, \con{s}( x ) \teq \con{s}( x-1 ) \bigr)$.
If \cvc's finite model finding mode for recursive functions is enabled (using the command line parameter ``--fmf-fun"),
then it will replace its list of known assertions based on the conversion $\conv$ before checking for satisfiability.
%If the functions provided in the input are admissible,
%then a ``satisfiable" response from the solver implies that a model exists for the original formula.
Accordingly, the solver will output an approximation of the interpretation for recursive function definitions,
that is, it may output the interpretation~(\ref{eq:approx-interp}) from Section~\ref{sec:encoding} for $s$.

>>>>

The translation modifies $\varphi$ in two main ways. First, it restricts the
quantification on function definitions for $\con{f}$ to the corresponding
uninterpreted type $\fargsort{\con{f}}$ and inserts appropriate coercions
$\fargx{\con{f}}{i}$. Second, it augments $\varphi$ with additional constraints
$\exists a : \fargsort{\con{f}}.\;\, \vecfarg{\con{f}}( a ) \teq \vec t$; these
ensure that the restricted definition for $\con{f}$ covers all relevant tuples
of terms, namely the ones for which an $\con{f}$ application exists and is
relevant to the satisfiability of $\varphi$.
%\jb{what does ``current branch of'' mean? can we drop it / rephrase it / vague
%it up?}

@@

{\small
\begin{verbatim}
(define-fun-rec s ((x Int)) Int (ite (<= x 0) 0 (+ x (s (- x 1)))))
(declare-fun c () Int)
(assert (> (s c) 100))
(check-sat)
\end{verbatim}
}

When reading this input,
\cvc adds the (annotated) quantified formula $\forallf{\con{s}} x.\;\, \con{s}( x ) \teq \lite\bigl( x \leq 0, 0, \con{s}( x-1 )\bigr)$ to its list of assertions,
which after rewriting becomes $\forallf{\con{s}} x.\;\, \lite\bigl( x \leq 0, \con{s}( x ) \teq 0, \con{s}( x ) \teq \con{s}( x-1 ) \bigr)$.
If \cvc's finite model finding mode for recursive functions is enabled (using the command line parameter ``--fmf-fun"),
then it will replace its list of known assertions based on the conversion $\conv$ before checking for satisfiability.
%If the functions provided in the input are admissible,
%then a ``satisfiable" response from the solver implies that a model exists for the original formula.
Accordingly, the solver will output the approximation of the interpretation it used for recursive function definitions,
that is, it will output the following model.
\ajr{prefer having the full output like this here?}
%it may output the interpretation~(\ref{eq:approx-interp}) from Section~\ref{sec:encoding} for $s$.

{\small
\begin{verbatim}
(model
(define-fun s (($x1 Int)) Int 
               (ite (= $x1 14) 105 (ite (= $x1 13) 91 (ite (= $x1 12) 78 
               (ite (= $x1 11) 66 (ite (= $x1 10) 55 (ite (= $x1 4) 10 
               (ite (= $x1 9) 45 (ite (= $x1 8) 36 (ite (= $x1 7) 28 
               (ite (= $x1 6) 21 (ite (= $x1 3) 6 (ite (= $x1 5) 15 
               (ite (= $x1 2) 3 (ite (= $x1 1) 1 0)))))))))))))))
(define-fun c () Int 14)
)
\end{verbatim}
}
